Against Spurious Understanding: Dovelating Inflated AI Claims \raisebox{-6pt}{\includegraphics[scale=0.09]{dove_1f54a-fe0f.png}}

### 2024-02-06 appendix.tex
removed brackets from file names for arxiv

\includegraphics[width=1.0\textwidth]{results/figures/measures_probe_CPI_(n_pc=128).png}

@@

\includegraphics[width=1.0\textwidth]{results/figures/measures_probe_PPI_(n_pc=128).png}

@@

\includegraphics[width=1.0\textwidth]{results/figures/measures_probe_UST_(1Mo)_(n_pc=128).png}

@@

\includegraphics[width=1.0\textwidth]{results/figures/measures_probe_UST_(1Yr)_(n_pc=128).png}

@@

\includegraphics[width=1.0\textwidth]{results/figures/measures_probe_UST_(10Yr)_(n_pc=128).png}

@@

\includegraphics[width=1.0\textwidth]{results/figures/measures_CPI_(n_pc=128).png}

@@

\includegraphics[width=1.0\textwidth]{results/figures/measures_PPI_(n_pc=128).png}

@@

\includegraphics[width=1.0\textwidth]{results/figures/measures_UST_(1Mo).png}

@@

\includegraphics[width=1.0\textwidth]{results/figures/measures_UST_(1Yr).png}

@@

\includegraphics[width=1.0\textwidth]{results/figures/measures_UST_(10Yr).png}

>>>>

\includegraphics[width=1.0\textwidth]{results/figures/measures_probe_CPI_n_pc=128.png}

@@

\includegraphics[width=1.0\textwidth]{results/figures/measures_probe_PPI_n_pc=128.png}

@@

\includegraphics[width=1.0\textwidth]{results/figures/measures_probe_UST_1Mo_n_pc=128.png}

@@

\includegraphics[width=1.0\textwidth]{results/figures/measures_probe_UST_1Yr_n_pc=128.png}

@@

\includegraphics[width=1.0\textwidth]{results/figures/measures_probe_UST_10Yr_n_pc=128.png}

@@

\includegraphics[width=1.0\textwidth]{results/figures/measures_CPI_n_pc=128.png}

@@

\includegraphics[width=1.0\textwidth]{results/figures/measures_PPI_n_pc=128.png}

@@

\includegraphics[width=1.0\textwidth]{results/figures/measures_UST_1Mo.png}

@@

\includegraphics[width=1.0\textwidth]{results/figures/measures_UST_1Yr.png}

@@

\includegraphics[width=1.0\textwidth]{results/figures/measures_UST_10Yr.png}
